Dusty galaxies and the degeneracy between their dust distributions and the attenuation formula

### 2015-04-28 paper.tex
Added Reddy discussion

We have nothing more than vague and conflicting ideas of dust distributions in
all high-redshift galaxies.  \citet{onodera10}, \citet{kashino13}, and 
\citet{price13} argue for nonuniform distributions in their samples, which
comprise dusty and dust-poor galaxies; \citet{erb06} present evidence for
uniform distributions in a similarly mixed sample.

@@

If we assume that dusty galaxies: (1) obey the \citet{calzetti00} attenuation
formula; and (2) were to all have the same UV spectrum in the absence of dust;
our results indicate that their H$\alpha$ and 0.66$\,\micron$ escape
fractions disagree.  Unlike low-redshift dust-poor galaxies, dusty galaxies
have \alephha~= \alephuvha$^{1.6}$; like low-redshift dust-poor galaxies,
dusty galaxies have nonuniform dust distributions.  The relations between
\alephha~and \alephuvha~are similar to those found by \citet{onodera10},
\citet{kashino13}, and \citet{price13} and conflict with those of
\citet{erb06}.  These studies assume the applicability of the \citet{calzetti00}
attenuation
formula, and use samples of high-redshift galaxies that are not necessarily
dusty.  Their UV escape fractions come from stellar population modeling, while
ours come from IRX; their H$\alpha$ escape fractions come from ratios of
averaged H$\alpha$ to averaged H$\beta$ luminosities, or ratios of H$\alpha$ to
UV luminosities, while ours come from assumptions about SFRs.

However, dusty galaxies may disobey the \citet{calzetti00} attenuation
formula, which complicates our interpretation of the more basic relation
between UV and 0.66$\,\micron$ escape fractions---the relation between
escape fractions for just the regions with nonionizing UV-emitting stars
\citep{reddy10,reddy12,buat11,buat12,penner12,kriek13}.  The true attenuation
formula for dusty galaxies may have a higher 0.66$\,\micron$ escape fraction
for a given UV escape fraction than does the \citet{calzetti00} formula.  A
formula modified according to
\citet{kriek13} with $\delta = -0.2$ and no bump at 0.2175$\,\micron$ has
\alephuvha~=
\alephuv$^{0.25}$ instead of \alephuvha~= \alephuv$^{0.33}$.  The combination of
this \citet{kriek13} formula and our result implies that
\alephha~= \alephuvha$^{2.2}$.  If the true formula instead has a
much lower 0.66$\,\micron$ escape fraction for a given UV escape
fraction than does the \citet{calzetti00} formula---say, \alephuvha~=
\alephuv$^{0.55}$---we conclude that for dusty
galaxies the H$\alpha$ and 0.66$\,\micron$ escape fractions agree.  Our
conclusion regarding the uniformity of dust distributions depends on the
assumed attenuation formula.  We cannot reject our hypothesis.  The
\citet{calzetti00} formula does demarcate the upper boundary of \alephha~for the
high-redshift dusty galaxies (bottom left panel of Fig. \ref{fha_fuv}), so
if it is the true formula then at least some dusty galaxies have uniform
dust distributions.  The unambiguous statement we make is that dusty galaxies
have relations between H$\alpha$ and UV escape fractions that are different from
the relation for low-redshift dust-poor galaxies.

@@

\begin{enumerate}
\item We measure H$\alpha$ line luminosities and limits, from
\emph{HST}/WFC3-IR grism spectra, for $z \sim 1$ galaxies with detected
100$\,\micron$ emission.  We determine rest-frame UV continuum power-law
indices ($\beta$ values) and ratios of IR to UV luminosities (IRX values).
\item For each galaxy we determine \alephuv, the escape fraction at
0.16$\,\micron$, from IRX.  We determine \alephha, the H$\alpha$ escape
fraction, from the H$\alpha$ luminosity and the total star formation rate.
\item For the \citet{overzier11} sample of low-redshift dust-poor galaxies, we
recover the \citet{calzetti97b} relation between H$\alpha$ and UV escape
fractions: \alephha~= \alephuv$^{0.80}$.  Our nonstandard method for determining
H$\alpha$ escape fractions should be grossly correct.
\item For the \citet{hwang13} sample of low-redshift dusty galaxies, we find
that \alephha~= \alephuv$^{0.55}$.
\item For our sample of dusty galaxies at $0.7 < z < 1.5$, we find that
\alephha~= \alephuv$^{0.55}$.  The dispersion about the best-fit relation is
large.
\item The interpretation of the results for dusty galaxies is unclear.  If we
assume that the \citet{calzetti00} attenuation formula applies to these
galaxies, our results agree with those of \citet{onodera10}, \citet{kashino13},
and \citet{price13} and conflict with those of \citet{erb06}: \alephha~=
\alephuvha$^{1.6}$.  They study
samples comprising dust-poor and dusty galaxies.  Dusty galaxies have
nonuniform dust distributions.  However, dusty galaxies may disobey the
\citet{calzetti00} attenuation formula.
\item Measurements of the ratios of H$\alpha$ to H$\beta$ luminosities may
decrease the dispersion in the relation between H$\alpha$ and UV escape
fractions for dusty galaxies at $z \sim 1$.  If the dispersion is real, these
galaxies have diverse dust distributions.
\end{enumerate}

@@

>>>>

We have nothing more than vague and conflicting ideas of dust distributions in
all high-redshift galaxies.  \citet{onodera10}, \citet{kashino13}, and 
\citet{price13} argue for nonuniform distributions in their samples, which
comprise dusty and dust-poor galaxies; \citet{erb06} present evidence for
uniform distributions in a similarly mixed sample.  \citet{reddy15} argue
that the uniformity of the dust distribution depends on the galaxy's
star formation rate: as the star formation rate increases the dust distribution
becomes less uniform.

@@

If we assume that dusty galaxies: (1) obey the \citet{calzetti00} attenuation
formula; and (2) were to all have the same UV spectrum in the absence of dust;
our results indicate that their H$\alpha$ and 0.66$\,\micron$ escape
fractions disagree.  Unlike low-redshift dust-poor galaxies, dusty galaxies
have \alephha~= \alephuvha$^{1.6}$; like low-redshift dust-poor galaxies,
dusty galaxies have nonuniform dust distributions.  The relations between
\alephha~and \alephuvha~are similar to those found by \citet{onodera10},
\citet{kashino13}, \citet{price13}, and \citet{reddy15} and conflict with those of
\citet{erb06}.  These studies assume the applicability of the \citet{calzetti00}
attenuation
formula, and use samples of high-redshift galaxies that are not necessarily
dusty.  Their UV escape fractions come from stellar population modeling, while
ours come from IRX; their H$\alpha$ escape fractions come from ratios of
averaged H$\alpha$ to averaged H$\beta$ luminosities, or ratios of H$\alpha$ to
UV luminosities, while ours come from assumptions about SFRs.

However, dusty galaxies may disobey the \citet{calzetti00} attenuation
formula, which complicates our interpretation of the more basic relation
between UV and 0.66$\,\micron$ escape fractions---the relation between
escape fractions for just the regions with nonionizing UV-emitting stars
\citep{reddy10,reddy12,reddy15,buat11,buat12,penner12,kriek13}.  The true attenuation
formula for dusty galaxies may have a higher 0.66$\,\micron$ escape fraction
for a given UV escape fraction than does the \citet{calzetti00} formula.  A
formula modified according to
\citet{kriek13} with $\delta = -0.2$ and no bump at 0.2175$\,\micron$ has
\alephuvha~=
\alephuv$^{0.25}$ instead of \alephuvha~= \alephuv$^{0.33}$.  The combination of
this \citet{kriek13} formula and our result implies that
\alephha~= \alephuvha$^{2.2}$.  The \citep{reddy15} attenuation formula has
\alephuvha~= \alephuv$^{0.23}$, implying that \alephha~= \alephuvha$^{2.4}$.
If the true formula instead has a
much lower 0.66$\,\micron$ escape fraction for a given UV escape
fraction than does the \citet{calzetti00} formula---say, \alephuvha~=
\alephuv$^{0.55}$---we conclude that for dusty
galaxies the H$\alpha$ and 0.66$\,\micron$ escape fractions agree.  Our
conclusion regarding the uniformity of dust distributions depends on the
assumed attenuation formula.  We cannot reject our hypothesis.  The
\citet{calzetti00} formula does demarcate the upper boundary of \alephha~for the
high-redshift dusty galaxies (bottom left panel of Fig. \ref{fha_fuv}), so
if it is the true formula then at least some dusty galaxies have uniform
dust distributions.  The unambiguous statement we make is that dusty galaxies
have relations between H$\alpha$ and UV escape fractions that are different from
the relation for low-redshift dust-poor galaxies.

@@

\begin{enumerate}
\item We measure H$\alpha$ line luminosities and limits, from
\emph{HST}/WFC3-IR grism spectra, for $z \sim 1$ galaxies with detected
100$\,\micron$ emission.  We determine rest-frame UV continuum power-law
indices ($\beta$ values) and ratios of IR to UV luminosities (IRX values).
\item For each galaxy we determine \alephuv, the escape fraction at
0.16$\,\micron$, from IRX.  We determine \alephha, the H$\alpha$ escape
fraction, from the H$\alpha$ luminosity and the total star formation rate.
\item For the \citet{overzier11} sample of low-redshift dust-poor galaxies, we
recover the \citet{calzetti97b} relation between H$\alpha$ and UV escape
fractions: \alephha~= \alephuv$^{0.80}$.  Our nonstandard method for determining
H$\alpha$ escape fractions should be grossly correct.
\item For the \citet{hwang13} sample of low-redshift dusty galaxies, we find
that \alephha~= \alephuv$^{0.55}$.
\item For our sample of dusty galaxies at $0.7 < z < 1.5$, we find that
\alephha~= \alephuv$^{0.55}$.  The dispersion about the best-fit relation is
large.
\item The interpretation of the results for dusty galaxies is unclear.  If we
assume that the \citet{calzetti00} attenuation formula applies to these
galaxies, our results agree with those of \citet{onodera10}, \citet{kashino13},
\citet{price13}, and \citet{reddy15} and conflict with those of \citet{erb06}: \alephha~=
\alephuvha$^{1.6}$.  They study
samples comprising dust-poor and dusty galaxies.  Dusty galaxies have
nonuniform dust distributions.  However, dusty galaxies may disobey the
\citet{calzetti00} attenuation formula.
\item Measurements of the ratios of H$\alpha$ to H$\beta$ luminosities may
decrease the dispersion in the relation between H$\alpha$ and UV escape
fractions for dusty galaxies at $z \sim 1$.  If the dispersion is real, these
galaxies have diverse dust distributions.
\end{enumerate}

@@

\bibitem[Reddy et al.(2015)]{reddy15} Reddy, N.~A., Kriek, M., 
Shapley, A.~E., et al.\ 2015, arXiv:1504.02782
